---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# parafit

<!-- badges: start -->
![GitHub R package version](https://img.shields.io/github/r-package/v/shaunson26/parafit)

<!-- badges: end -->

The goal of parafit is to ...

## Installation

You can install the development version of parafit from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Shaunson26/parafit")
```

```{r, echo=F, include = F}
devtools::load_all()
```


Functions of the `parafit` package have the suffix `pf_` e.g.

``` r
pf_pcoa
pf_parafit
```

## Example

Create Principal Coordinates of phylogentic distances.

```{r}
# gopher.D and lice.D are included in parafit and are square distance matrices
gopher_pcoa <- pf_pcoa(gopher.D)
lice_pcoa <- pf_pcoa(lice.D)

gopher_pcoa[1:5, 1:3]
lice_pcoa[1:5, 1:3]
```

Run parafit obtaining the global test statistics and testing individual associations

```{r}
res <-
  pf_parafit(host_pcoa = t(gopher_pcoa),
             parasite_pcoa = lice_pcoa,
             associations = gopher.lice.links,
             permutations = 999,
             test_links = TRUE)

res
```

For larger datasets, testing individual associations can be run in parallel

```{r}
res <-
  pf_parafit(host_pcoa = t(gopher_pcoa),
             parasite_pcoa = lice_pcoa,
             associations = gopher.lice.links,
             permutations = 999,
             test_links = TRUE,
             parallel = TRUE,
             cores = 2)

res
```


